Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-17 WRITEUP/ms.tex
add R32 to CO32 section

@@

At the position of \cco, continuum emission is not detected in
the line-free channels down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.
The continuum is buried within the sensitivity limit of this data.
% (consistent with the Gaussian + poly fit to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
% line free channels:1, 118, 160, 600
% nchan =(117+600-160+1) = 558
% sigma =  0.83 mJy/B

2mm: resolved along the major axis, but unresolved along the minor axis. We decomposed the continuum from the foreground and background sources by subtracting a point
source model in the $uv-$plane (see Riechers+13 SMMJ04135 description)

>>>>

Assuming the spatial extents between \bco and \cco are similar and therefore
a negligible differential lensing effect, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66$\pm$0.41.
The high uncertainty is dominated by the uncertainties in the \cco line
intensity.

@@

No continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.
% (consistent with the Gaussian + poly fit to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
% line free channels:1, 118, 160, 600
% nchan =(117+600-160+1) = 558
% sigma =  0.83 mJy/B

We detect \pdbi 2\,mm continuum in \Fig{2mm}. The integrated flux density is
1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
centered on the lensing galaxy. A slightly extended emission is seen
also along the lensed arc. This suggests that the detected emission is
toward both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.

We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
in the residual coincides with the lensed arc, and is also consistent with
the difference between the integrated and the peak flux
in the original continuum map ($\sim$0.4 mJy). We therefore adopt this as
emission toward the background galaxy.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
\caption{
An overlay of the 2\,mm continuum emission on the optical image. Contours start at ...
\label{fig:2mm}}
\end{figure}
